An algorithm for finding the global extremum\\ of a partially defined function\thanks{This work was supported by the Russian Science Foundation, project No. 21-11-00204.}

### 2023-08-31 2023/MMST/samplepaper.tex
some fixes

First, the objective function may be multiextremal, nondifferentiable, and, moreover, defined in the form of a ``black box'' (i.e. in the form of some subroutine, which entry the argument is supplied to, and the output is respective function value).
Second, each computing of the function at some point of the feasible region may require considerable computation resources.

@@

The experts in Data Science have proposed various approaches to the imputation (restoring) of the missing data:
\begin{itemize}
  \item Deleting of all cases, which have missing values of some variables (at the worst, the algorithm loses the access to the useful information contained in the on-missing observations’ values);
  \item Replacing any missing value with the average of the available values of the variable (doesn’t work with the qualitative variables, doesn’t account for the correlation of the data);
  \item Replacing by the most frequent value or by a constant (differs from the use of the median only by the ability to work with the qualitative parameters);
  \item Replacing the data using the method of $k$ nearest neighbors (unlike the former, accounts for the correlation between the parameters, sensitive to the fadeouts, computation costly);
  \item Multiple imputation by chained equations (MICE) -- imputation of each value is performed not one but many times (allows understanding how reliable or unreliable is the value suggested);
  \item Imputation of the data using a deep learning (restores the missing values by means of training a neural network on the points, for which all parameters are available, computation costly for big data).
\end{itemize}

@@

Each series of experiments consisted of 100 GKLS problems with everywhere computable objective function (the original GKLS problems), 100 problems with the non-computabilities at the boundaries of the search domains, and 100 problems with non-computability regions defined randomly.

>>>>

First, the objective function may be multiextremal, non-differentiable, and, moreover, defined in the form of a ``black box'' (i.e. in the form of some subroutine, which entry the argument is supplied to, and the output is respective function value).

Second, each computing of the function at some point of the feasible region may require considerable computation resources.

@@

The experts in Data Science have proposed various approaches to the imputation (restoring) of the missing data:
\begin{itemize}
  \item Deleting of all cases, which have missing values of some variables (at the worst, the algorithm loses the access to the useful information contained in the on-missing observations’ values);
  \item Replacing any missing value with the average of the available values of the variable (doesn’t work with the qualitative variables, doesn’t account for the correlation of the data);
  \item Replacing by the most frequent value or by a constant (differs from the use of the median only by the ability to work with the qualitative parameters);
  \item Replacing the data using the method of $k$-nearest neighbors (unlike the former, accounts for the correlation between the parameters, sensitive to the fadeouts, computation costly);
  \item Multiple imputation by chained equations (MICE) -- imputation of each value is performed not one but many times (allows understanding how reliable or unreliable is the value suggested);
  \item Imputation of the data using a deep learning (restores the missing values by means of training a neural network on the points, for which all parameters are available, computation costly for big data).
\end{itemize}

@@

Each series of experiments consisted of 100 GKLS problems with everywhere computable objective function (original), 100 problems with the non-computabilities at the boundaries of the search domains (round), and 100 problems with non-computability regions defined randomly (random).
